\chapter{Modules}

\section{UI : Web}
	\subsection{Exercise tools}
		This module contains every tools to edit an exercise.
	\subsection{Widget}
		This module contains various tool for a user friendly navigation.
	\subsection{Notifications}
		This module informs about every new information (new exercises, remaining exercises ...).
	\subsection{User}
		This module contains web view for user information (rank, profiles, mailbox ...).

\section{UI : Text-based}
	\subsection{Exercise tools}
		This module contains every tools to edit an exercise.	
	\subsection{User}
		This module contains text-based view for user information (rank, profiles, mailbox ...).
	\subsection{Notifications}
		This module informs about every new information (new exercises, remaining exercises ...).
		
\section{Services : HTTP}
	\subsection{Redirection}
		This module links the UI layer with the Core layer though the HTTP services.

\section{Core : Dojo logic}
	\subsection{Exercise}
		This module orchestrates various other module to establish an exercise.
	\subsection{Description}
		This module is the language used to write an exercise.
	\subsection{Grade}
		This module contains the evaluation system and exercise correction.
	\subsection{User}
		This module contains user data (access rights, profiles, mailbox ...).  
	\subsection{Data Analysis}	
		This module analyzes 
	\subsection{Notifications}
	 	This module informs users about their new or remaining task.
		
\section{Core : Machinist}
	\subsection{MachineProvider}
		This module is a sandbox provider.
	\subsection{Sandbox}
		This module is a closed environment given to the dojo logic, it can be from a virtual or a physical machine.

\section{Core : Reactive}
	\subsection{Entity}
		This module manages update and change between various exercise state.
	\subsection{Event}
		This module gives the type of event for an entity to be updated.
	\subsection{Dependency}
		This module handles dependencies between entity for chain reaction.
		 
\section{Core : VFS}
	\subsection{Source}
		This module takes care of source file generated by the dojo logic layer.
	\subsection{Backup}
		This module makes a backup of every entity states.
		
		
		